---
title: "DengAI: Predicting Disease Spread"
author: "Rupam Das"
date: "December 2, 2017"
output: word_document
---

Loading the packages into 

```{r}
library(plyr)
library(dplyr)
library(fpp)
library(caret)
library(tidyquant)
library(ggplot2)
library(imputeTS)
library(MASS)
library(forecast)
library(rsample)
```

Importing the data into R evnironment

```{r Importing data}
train <- read.csv("C:/Education/PredictiveAnalysis/DengAI/dengue_train.csv")
train_results <- read.csv("C:/Education/PredictiveAnalysis/DengAI/dengue_labels_train.csv")
complete_train <- train %>% mutate(total_cases = train_results[,4])
test <- read.csv("C:/Education/PredictiveAnalysis/DengAI/dengue_features_test.csv")
```

Replacing NAs

```{r Mydataset}
my_data <- complete_train
my_data$ndvi_ne <- na.interpolation(my_data$ndvi_ne, option="spline")
my_data$ndvi_nw <- na.interpolation(my_data$ndvi_nw, option="spline")
my_data$ndvi_se <- na.interpolation(my_data$ndvi_se, option="spline")
my_data$ndvi_sw <- na.interpolation(my_data$ndvi_sw, option="spline")
my_data$precipitation_amt_mm <- na.interpolation(my_data$precipitation_amt_mm, option="spline")
my_data$reanalysis_air_temp_k <- na.interpolation(my_data$reanalysis_air_temp_k, option="spline")
my_data$reanalysis_avg_temp_k <- na.interpolation(my_data$reanalysis_avg_temp_k, option="spline")
my_data$reanalysis_dew_point_temp_k <- na.interpolation(my_data$reanalysis_dew_point_temp_k, option="spline")
my_data$reanalysis_max_air_temp_k <- na.interpolation(my_data$reanalysis_max_air_temp_k, option="spline")
my_data$reanalysis_min_air_temp_k <- na.interpolation(my_data$reanalysis_min_air_temp_k, option="spline")
my_data$reanalysis_precip_amt_kg_per_m2 <- na.interpolation(my_data$reanalysis_precip_amt_kg_per_m2, option="spline")
my_data$reanalysis_relative_humidity_percent <- na.interpolation(my_data$reanalysis_relative_humidity_percent, option="spline")
my_data$reanalysis_sat_precip_amt_mm <- na.interpolation(my_data$reanalysis_sat_precip_amt_mm, option="spline")
my_data$reanalysis_specific_humidity_g_per_kg <- na.interpolation(my_data$reanalysis_specific_humidity_g_per_kg, option="spline")
my_data$station_avg_temp_c <- na.interpolation(my_data$station_avg_temp_c, option="spline")
my_data$station_diur_temp_rng_c <- na.interpolation(my_data$station_diur_temp_rng_c, option="spline")
my_data$station_max_temp_c <- na.interpolation(my_data$station_max_temp_c, option="spline")
my_data$station_min_temp_c <- na.interpolation(my_data$station_min_temp_c, option="spline")
my_data$station_precip_mm <- na.interpolation(my_data$station_precip_mm, option="spline")
my_data$reanalysis_tdtr_k <- na.interpolation(my_data$reanalysis_tdtr_k, option="spline")

```

Correlation among columns
```{r}
cor(my_data)
```


Seperate the data by cities

```{r Dividing my data}
sj_data <- my_data %>% filter(city == "sj")
iq_data <- my_data %>% filter(city == "iq")
```

```{r removing-columns}
sj_data <- sj_data[,-c(1,4)]
iq_data <- iq_data[,-c(1,4)]
```

# SJ DATA

```{r removing-coulmns-correlated}
sj_data <- sj_data[,-c(8:12)]
sj_data <- sj_data[,-c(13)]
iq_data <- iq_data[,-c(8:12)]
iq_data <- iq_data[,-c(13)]
```

Splitting the training data in 80:20

```{r data-split}
set.seed(100)
train_test_split <- initial_split(sj_data, prop = 0.8)
train_sj <- training(train_test_split)
test_sj  <- testing(train_test_split) 

```

fitting a model for train data
```{r model-1}
fit <- lm(total_cases~., train_sj)
summary(fit)
plot(fit)
abline(fit)
```

predicting the model

```{r predit-model-1}
x <- predict(fit,test_sj)
View(x)
cor(x,test_sj$total_cases)
```


```{r nas}

#test[, 1:ncol(test)][is.na(test[, 1:ncol(test)])] <- 0
test$ndvi_ne <- na.interpolation(test$ndvi_ne, option="spline")
test$ndvi_nw <- na.interpolation(test$ndvi_nw, option="spline")
test$ndvi_se <- na.interpolation(test$ndvi_se, option="spline")
test$ndvi_sw <- na.interpolation(test$ndvi_sw, option="spline")
test$precipitation_amt_mm <- na.interpolation(test$precipitation_amt_mm, option="spline")
test$reanalysis_air_temp_k <- na.interpolation(test$reanalysis_air_temp_k, option="spline")
test$reanalysis_avg_temp_k <- na.interpolation(test$reanalysis_avg_temp_k, option="spline")
test$reanalysis_dew_point_temp_k <- na.interpolation(test$reanalysis_dew_point_temp_k, option="spline")
test$reanalysis_max_air_temp_k <- na.interpolation(test$reanalysis_max_air_temp_k, option="spline")
test$reanalysis_min_air_temp_k <- na.interpolation(test$reanalysis_min_air_temp_k, option="spline")
test$reanalysis_precip_amt_kg_per_m2 <- na.interpolation(test$reanalysis_precip_amt_kg_per_m2, option="spline")
test$reanalysis_relative_humidity_percent <- na.interpolation(test$reanalysis_relative_humidity_percent, option="spline")
test$reanalysis_sat_precip_amt_mm <- na.interpolation(test$reanalysis_sat_precip_amt_mm, option="spline")
test$reanalysis_specific_humidity_g_per_kg <- na.interpolation(test$reanalysis_specific_humidity_g_per_kg, option="spline")
test$station_avg_temp_c <- na.interpolation(test$station_avg_temp_c, option="spline")
test$station_diur_temp_rng_c <- na.interpolation(test$station_diur_temp_rng_c, option="spline")
test$station_max_temp_c <- na.interpolation(test$station_max_temp_c, option="spline")
test$station_min_temp_c <- na.interpolation(test$station_min_temp_c, option="spline")
test$station_precip_mm <- na.interpolation(test$station_precip_mm, option="spline")
test$reanalysis_tdtr_k <- na.interpolation(test$reanalysis_tdtr_k, option="spline")
```

dividing original test data for different cities
```{r test-data}
sj_test_data <- test %>% filter(city == "sj")
iq_test_data <- test %>% filter(city == "iq")
sj_test_data <- sj_test_data[,-c(1,4)]
sj_test_data <- sj_test_data[,-c(8:12)]
sj_test_data <- sj_test_data[,-c(13)]
iq_test_data <- iq_test_data[,-c(1,4)]
iq_test_data <- iq_test_data[,-c(8:12)]
iq_test_data <- iq_test_data[,-c(13)]
```

replacing NAs in test data with 0

fitting and predicting complete model for entire train data

```{r full-model-1}
fit_sj <- lm(total_cases~., sj_data)
summary(fit_sj)

x <- predict(fit_sj,sj_test_data)
write.csv(x,"sj.csv")

fit_iq <- lm(total_cases~., iq_data)
summary(fit_iq)

y <- predict(fit_iq,iq_test_data)
write.csv(y,"iq.csv")
```

#STEP AIC final submission


```{r full-model-1}
fit_sj <- lm(total_cases~., sj_data)
autofit_sj <- stepAIC(fit_sj)

x <- predict(autofit_sj,sj_test_data)
write.csv(x,"sj.csv")

fit_iq <- lm(total_cases~., iq_data)
autofit_iq <- stepAIC(fit_iq)

y <- predict(autofit_iq,iq_test_data)
write.csv(y,"iq.csv")

```
